Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-18 BN_discretizer_paper.tex
Correct English mistakes

\begin{table}[h]
  \centering
  \caption{Discretization results of Auto MPG dataset based on the graph in Fig. \ref{fig:auto_graph_1} by the three methods. The first to fifth row are discretization edges on each continuous variable. The sixth row is the log-likelihood of the dataset based on the discretization results. The discretization result for the heuristic matches that for the optimal Bayesian approach. The MDL method is less sensitive to distribution of values of other variables and fails to return discretization edges.}
  \input{table_autoMPG_1.tex}
  \label{table:auto_disc_table_1}
\end{table}

@@

\begin{table}
  \centering
  \caption{Discretization results of Wine dataset based on the graph Fig. \ref{fig:wine_graph_1} by the three different method. The first to the thirteenth row are discretization edges on each continuos variable. The fourteenth row is the log-likelihood of the dataset based on the discretization results. The optimal Bayesian approach has the best discretization result in terms of likelihood. The heuristic method obtains a result nearly as good as the Bayesian approach. The MDL method discretizes more than half of continuous variables but still does not discretize enough intervals. Some discretization edges appear in the results of all three methods, and indicate that they are the most determinant edges.}
  \scalebox{1.0}{
  \input{table_wine_1.tex}
  }
  \label{table:wine_disc_table_1}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \caption{Discretization results of Auto MPG dataset based on the graph in Fig. \ref{fig:auto_graph_1} by the three methods. The first five rows are discretization edges on each continuous variable. The sixth row is the log-likelihood of the dataset based on the discretization results. The discretization result for the heuristic matches that for the optimal Bayesian approach. The MDL method is less sensitive to distribution of values of other variables and fails to return discretization edges.}
  \input{table_autoMPG_1.tex}
  \label{table:auto_disc_table_1}
\end{table}

@@

\begin{table}
  \centering
  \caption{Discretization results of Wine dataset based on the network in Fig. \ref{fig:wine_graph_1} by the three different methods. The first thirteen rows are discretization edges on each continuos variable. The fourteenth row is the log-likelihood of the dataset based on the discretization results. The optimal Bayesian approach has the best discretization result in terms of likelihood. The heuristic method obtains a result nearly as good as the Bayesian approach. The MDL method discretizes more than half of continuous variables but still does not discretize enough intervals. Some discretization edges appear in the results of all three methods, and indicate that they are the most determinant edges.}
  \scalebox{1.0}{
  \input{table_wine_1.tex}
  }
  \label{table:wine_disc_table_1}
\end{table}
